14th International Satisfiability Modulo Theories Competition (SMT-COMP 2019): Rules and Procedures

### 2019-04-19 rules/rules19.tex
fix a todo

Solvers will be publicly evaluated in all tracks and divisions into
which they have been entered.  All results of the competition will be
made public.
\todo{Giles: Include licence information - minimum requirement: licence must allow to run the binary for evaluation purposes}
\an{intro of the section maybe, we should add there that solvers will be archived on the website and so on. Interestingly, we replied to the reviewer in the report that the solvers are publicly available in the StarExec space when asked about reproducability, but in the past it was never defined under which terms.}

>>>>

Solvers will be publicly evaluated in all tracks and divisions into
which they have been entered.  All results of the competition will be
made public. Solvers will be made publicly available after the competition and it is a minimum licence requirement that (i) solvers can be distributed in this way, and (ii) all submitted solvers may be freely used for academic evaluation purposes.

%\an{intro of the section maybe, we should add there that solvers will be archived on the website and so on. Interestingly, we replied to the reviewer in the report that the solvers are publicly available in the StarExec space when asked about reproducability, but in the past it was never defined under which terms.}
